---
title: "Irish_Jobs"
author: "Nkirote"
date: "19/04/2021"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
 
Load libraries needed for this task

```{r}
library(rvest)
library(dplyr)
```

Scraper function for extracting data from the website

```{r}
scraper <- function(url,selector,output = "text",all_nodes = TRUE) {
  
  content <- read_html(url) 
  
  if (all_nodes){
    nodes <- content %>%
      html_nodes(selector)
  }else{
   nodes <- content %>%
     html_node(selector)
  }
  
  if (output == "text") {
    extracted_data <- nodes %>%
      html_text()
  }else if(output == "table"){
    extracted_data <- nodes %>%
      html_table()
  }else if (output == "attrs") {
    extracted_data <- nodes %>% 
      html_attrs()
  }else{
    extracted_data <- nodes %>%
      html_attr(output)
  }
  
 return(extracted_data)
}

```

Initial dataframe
```{r}
df <- data.frame(irish_top_company_names = c(), total_review_scores = c(), reviewer_status = c(), reviewer_location = c(), reviewer_headlines = c())
```

Extract the companies and their attributes, including ; 
a. Name of the Company
b. Review category and their scores
c. Date of review
d. Reviewers Information (i.e. Job title,  Employment Status, Location)

i. Scrape the company names

```{r}
irish_top_company_names <- scraper(url = "https://www.irishjobs.ie/company-reviews", selector = ".sky-top-company__box-name")
irish_top_companies_names
```

ii. Scrape review categories and their scores

```{r}
total_review_scores <- scraper(url = "https://www.irishjobs.ie/company-reviews" , selector = ".sky-top-company__box-rating")

total_review_scores <- as.numeric(str_split(total_review_scores, "/", simplify = TRUE)[,1])
total_review_scores
```

iii. Scrape reviewer's info

```{r}
library(stringr)
reviewers_info <- scraper(url = "https://www.irishjobs.ie/company-reviews", selector = ".sky-top-company__box-details")
reviewers_info
group_1 <- str_split(reviewers_info[c(1:6,10)], " in ", simplify = TRUE)
group_1_status <- group_1[,1]

group_2 <- str_split((reviewers_info[7:9]), " in ", n = -1, simplify = TRUE)
group_2_status <- str_c(group_2[,1],group_2[,2], sep = " in ")

reviewer_status <- c(group_1_status, group_2_status)
reviewer_status

reviewer_location <- str_split(c(group_1[,2], group_2[,3]), ",", simplify = TRUE)[,1]
reviewer_location
  
```
iv. Scrape the reviewer's headline

```{r}
reviewer_headlines <- scraper(url = "https://www.irishjobs.ie/company-reviews", selector = ".sky-top-company__box-headline")

reviewer_headlines <- str_replace_all(reviewers_headline, '\"', "")
reviewer_headlines
```
v. Join all the above vectors to form a dataframe for 10 Irish top company review information

```{r}
x <- as.data.frame(cbind(irish_top_company_names, total_review_scores, reviewer_status, reviewer_location, reviewer_headlines))

irish_top_company_reviews <- rbind(df,x)
irish_top_company_reviews

```



